---
title: "R绘制漂亮的图一"
author: "刘伟"
date: '2021-04-12'
output: pdf_document
---

## Table of Content {#toc}

* [普通plot绘图](#ordiPlot)
* [ggplot绘图](#ggplot)
* [Work on scale of  axis](#yscale)
* [Work on layout](#layout)
* [Work on colors](#colors)
* [Auto save many figures](#autoSaveFig)
* [Work on theme](#theme)

## 普通plot绘图{#ordiPlot}

### 绘制折线图

绘制折线图，并设置合适的坐标字体
```{Rmd}
par(mar=c(4.8,4.8,2,2))
plot(1:(n_egv-1), egrat, type='o', xlab='q', ylab='eigv. ratio', lwd=3, cex.axis = 1.6, cex.lab=1.8)
grid(col=1, lwd=2, lty=2)
```

### 坐标轴标签旋转绘图
```{Rmd}
par(mar=c(6,6,2,2))
plot(1:nrow(dat_Tr_sort_inter), axes=F,
     dat_Tr_sort_inter$total_trainhours[order_Tr], 
     type='o', xlab='', ylab='Total_hours', lwd=3, cex.axis = 1.6, cex.lab=1.8)
grid(col=1, lwd=2, lty=2)
axis(1, 1:nrow(dat_Tr_sort_inter),labels=dat_Tr_sort_inter$Enames[order_Tr],
     las  = 2)
axis(2)
```



### 4 怎么添加图像的形状参数，有的曲线有形状，有的曲线没有形状，没有形状的曲线用-1表示
```{Rmd}
legend('topleft', c('真实曲线', '预测曲线', '拐点时间'), col=c(1,2,4), lty=1, pch=c(1,-1,-1))
```

### 5. R绘制长度不同的向量的箱线图
```{Rmd}
Rt_list <- list(Rt_Pro, Rt_Hubei, Rt_Wuhan, Rt_Japan, Rt_Skorea, Rt_Sing, Rt_Italy)
boxplot(Rt_list, ylim=c(0,5.2), names = c('China', 'Hubei', 'Wuhan', 'Japan', 'SKorea', 'Singapore',
                                          'Italy'))
abline(h=1, lty=3,col='green4')
```

### 6. 添加没有边框的图例：利用bty='n'
```{Rmd}
plot(1: (nr-id_vec[1]+ 1-time), ratio7(dat[(id_vec[1]): nr,1], time), 
       xlim=xlim, ylim=ylim, col=1,
       type='o', xlab='Day', ylab='ratio')
  for(k in 2: nc){
    lines(1: (nr-id_vec[k]+ 1-time), ratio7(dat[(id_vec[k]): nr,k], time), col=k)
    points(1: (nr-id_vec[k]+ 1-time), ratio7(dat[(id_vec[k]): nr,k], time), col=k, pch=k)
  }
  abline(h =1 ,col=1, lty=2)
  legend('topright', names(dat), col=1:nc, pch=1:nc,lty=1, bty='n')

```


[↑ 返回目录页](#toc)<br><br>

## 2 漂亮美观强大的ggplot2绘图技术{#ggplot}

### Basic plots
1 绘制箱线图
```{r}
datafun <- function(mat1, mat2, xname, methodname){
  n1 <- dim(mat1)[1];
  n2 <- dim(mat2)[1];
  p <- dim(mat1)[2];
  suml <- (n1 + n2)*p
  data = as.data.frame(matrix(0, suml, 1))
  for(i in 1:p){
    data[((i - 1)*n1 + 1):(n1*i), 1] <- mat1[, i]
  }
  for(j in 1:p){
    data[(n1*p + (j - 1)*n2 + 1):(n1*p + n2*j), 1] <- mat2[, j]
  }
  colnames(data) = "Value"; 
  data$method = c(rep(methodname[1],  n1*p), rep(methodname[2], n2*p))
  data$snp_sparse =  c(rep(xname, each = n1), rep(xname, each = n2))
  return(data)
}
library("mvtnorm")
library("ggplot2")
n1 <- 50;
n2 <- 100;
p <- 4;
mat1 <- rmvnorm(n1, mean = rep(0, p), sigma = diag(p), method = "chol");
mat2 <- rmvnorm(n1, mean = rep(0, p), sigma = diag(p), method = "chol");
xname = c("0.2", "0.3", "0.4", "0.5");
methodname = c("method1","method2");
dat <- datafun(mat1, mat2, xname, methodname)
# 按照x的值分组画箱线图，并设置坐标字体大小
ggplot(dat, aes(x=snp_sparse, y=Value, fill=method)) + geom_boxplot(aes(fill=method)) +
  theme(axis.text.x = element_text(size = 12, angle=70, vjust=0.6)
,axis.text.y = element_text(size = 18),plot.title = element_text(hjust = 30,vjust=-40,size=14) 
,legend.position="none") +ylim(c(0,2))
```


2 利用ggplot2画折线图

```{r}
elboPlot <- function(elbo_seq){
  library(ggplot2)
  p1 <- ggplot(data=data.frame(ELBO= elbo_seq, iter=1:length(elbo_seq)),
               aes(x=iter, y=ELBO))
  
  p1 + geom_line(size=2) + ggtitle("VB algorithm") +
    theme(plot.title = element_text(hjust = 0.5),
          axis.text.x=element_text(size=14,color="red"),
          axis.text.y=element_text(size=14, color="green"),
          axis.title.x = element_text(size=18, color='black'),
          axis.title.y = element_text(size=18, color='black'),
          title= element_text(size=20, color='blue')
    ) 
}
elboPlot(elbo_seq = 1:100)

single_line_Plot <- function(y, x=NULL, x.name="iter", y.name="logLik",
                             title.name="Title",title.col="black", title.size=20, x.axis.col='black', x.axis.size=14, y.axis.col='black', y.axis.size=14, xlab.size=18, ylab.size=18, line.size=2){
  library(ggplot2)
  if(is.null(x)) x <- 1:length(y)
  if(length(x) != length(y)) stop("x and y must have same length!")
  p1 <- ggplot(data=NULL,
               aes(x=x, y=y))
  
  p1 + geom_line(size=line.size) + ggtitle(title.name) + xlab(x.name) + ylab(y.name) +
    theme(plot.title = element_text(hjust = 0.5),
          axis.text.x=element_text(size=x.axis.size,color=x.axis.col),
          axis.text.y=element_text(size=y.axis.size, color=y.axis.col),
          axis.title.x = element_text(size=xlab.size, color='black'),
          axis.title.y = element_text(size=ylab.size, color='black'),
          title= element_text(size=title.size, color=title.col)
    ) 
}
single_line_Plot(1:10)


```

[↑ 返回目录页](#toc)<br><br>
### Work on scale of  axis{#yscale}

```{Rmd}
simutool::boxPlot(y=timeMat, title.name = " ",y.name = 'Time(sec.)') +  scale_y_log10()
```
[↑ 返回目录页](#toc)<br><br>

### Work on layout{#layout}
类似par(mfrow=c(2,2))的用法包：
```{Rmd}
library(grid)
grid.newpage()
pushViewport(viewport(layout = grid.layout(2,2)))
print(p1, vp = viewport(layout.pos.row = 1, layout.pos.col = 1))
print(p2, vp = viewport(layout.pos.row = 1, layout.pos.col = 2))
print(p3, vp = viewport(layout.pos.row = 2, layout.pos.col = 1))
print(p4, vp = viewport(layout.pos.row = 2, layout.pos.col = 2))
```
Or use the patchwork package
```{Rmd}
library(patchwork)
p <- p1+p2+p3+p4 + 
   plot_layout(byrow = T, nrow=2, ncol=2)
```
[↑ 返回目录页](#toc)<br><br>

### Work on colors{#colors}
```{Rmd}
cols <- c("antiquewhite2", "dodgerblue2","palegreen2","goldenrod2","red",
          "antiquewhite4","dodgerblue4","palegreen4","goldenrod4",
          "blue4", "brown")
# check the color codes
library(colorspace)
ramp.list = adjust_transparency(cols,   alpha = 0.6) # Check the color codes in the specified transparency.
ramp.list
# plot the color bar to check the colors
barplot(rep(1, length(ramp.list)), axes = FALSE, space = 0, col = ramp.list)

cols[-5] <- ramp.list[-5] # save the colors we required.
manul_fill_col <- scale_fill_manual(values = cols)
# Then plot
p1   + geom_violin(trim=FALSE, scale = "width" )+
  geom_boxplot(width=0.1, fill="white") +  facet_wrap(PCs~Error,scales= "free" ) + labs(x=NULL)+ 
  scale_x_discrete(breaks = NULL) + manul_fill_col +
  thmem_used 
```

ggsci is a wonderful colors platte package, which can help you choose color automatically.
ggcsi配色网址：
http://www.sci666.net/60850.html
```{Rmd}
library(ggsci) 
library(patchwork)
g1 <- clusterPlot(dlpfc2, label=clusters[-na_id], palette=NULL, size=0.05) 
  
p1 <- g1 + scale_fill_jco() + labs(title= 'JCO') + guides(fill=F)
p2 <- g1 + scale_fill_npg() + labs(title= 'Nature')
p3 <- g1 + scale_fill_aaas()+ labs(title= 'Science')
p4 <- g1 +  scale_fill_nejm()+ labs(title= 'NEJM')
 p1 + p2 + p3 + p4
p5 <- g1 + scale_fill_lancet() + labs(title= 'Lancet')
p6 <- g1 + scale_fill_jama() + labs(title= 'JAMA')
p7 <- g1 +  scale_fill_d3() + labs(title= 'd3')
p8 <- g1 +   scale_fill_ucscgb()+ labs(title= 'UCSCGB')
p5 + p6 + p7 + p8
p5 <- g1 + scale_fill_locuszoom() + labs(title= 'Locuszoom')
p6 <- g1 + scale_fill_igv() + labs(title= 'IGV')
p7 <- g1 +  scale_fill_startrek() + labs(title= 'Startrek')
p8 <- g1 +   scale_fill_uchicago()+ labs(title= 'Uchicago')
p5 + p6 + p7 + p8

```

[↑ 返回目录页](#toc)<br><br>

### Auto save many figures{#autoSaveFig}

Ordinary plot in R
```{Rmd}
# filepath <- 'IncreasedModellingFiles/Model6_HuBei_Guaipoints/'
for(k in 1:n.HuBei){
  
  # jpeg(file = paste0(filepath, '/', row.names(Zkt.HuBei)[k], '.jpg')) # 保存为jpg
  pdf(file = paste0(filepath, '/', row.names(Zkt.HuBei)[k], '.pdf')) #保存为pdf
  plot(cum_quezhen_pred[k, ], axes = F ,type='l', main=row.names(Zkt.HuBei)[k],
       ylab='cum. identified illness', xlab='Date',col=2, lty=2)
  lines(cum_quezhen[k,], col=1)
  points(cum_quezhen[k,], col=1)
  v1_tmp <- which(colnames(Zkt_pred) == guaipoint_vec[k])
  abline(v=v1_tmp, col = 'blue')
  text(x=v1_tmp, y=cum_quezhen_pred[k, round(TT.HuBei/2)],
       guaipoint_vec[k])
  axis(1, 1:ncol(Zkt_pred),labels= colnames(Zkt_pred))
  axis(2)
  grid()
  dev.off()
} 
```

ggplot2:
```{Rmd}
filepath <- "D:\\LearnFiles\\Research paper\\ProPCA\\RealData"
n_ID <- length(name_ID12)
for(j in 1: n_ID){
  
  cat('brain ', j, '\n')
  
  clusters <- list()
  clusters[[1]] <- clusterList12[[j]]$SSDRcluster
  clusters[[2]] <- clusterList12[[j]][[paste0('BayesSpace', clustNumMat[j,3])]]
  clusters[[3]] <- clusterList12[[j]]$GMRF
  
  dlpfc <- readRDS(paste0("humanbrain\\", name_ID12[j],".rds") ) 
  clusters[[4]] <- dlpfc@colData$layer_guess_reordered
  na_id <- which(is.na(clusters[[4]]))
  names(clusters) <- c("SSDRcluster", 'BayesSpace', "GMRF", "Groundtruth")
  library(BayesSpace)
  library(ggplot2)
  
  ## Plot the figures we require to save.
  dlpfc2 <- dlpfc[,-na_id] # dropout the missing values
  p1 <- clusterPlot(dlpfc2, label=clusters[[4]][-na_id], palette=NULL, size=0.05) +
    scale_fill_viridis_d(option = "A", labels = 1:clustNumMat[j,1]) +
    labs(title="groundtruth")
  
  p2 <- clusterPlot(dlpfc2, label= as.factor(clusters[["SSDRcluster"]][-na_id]), palette=NULL, size=0.05) +
    scale_fill_viridis_d(option = "A", labels = 1:clustNumMat[j,2]) +
    labs(title=paste0("SSDRcluster: ARI=", round(AriMat[j,1],2)))
  
  
  p3 <- clusterPlot(dlpfc2, label= as.factor(clusters[["BayesSpace"]][-na_id]), palette=NULL, size=0.05) +
    scale_fill_viridis_d(option = "A", labels = 1:clustNumMat[j,3]) +
    labs(title=paste0("BayesSpace",clustNumMat[j,3],": ARI=", round(AriMat[j,2],2)))
  
  p4 <- clusterPlot(dlpfc2, label= as.factor(clusters[["GMRF"]][-na_id]), palette=NULL, size=0.05) +
    scale_fill_viridis_d(option = "A", labels = 1:clustNumMat[j,4]) +
    labs(title=paste0("GMRF: ARI=", round(AriMat[j,3],2)))
  # pdf(file =) #保存为pdf
  # layout the multiple figures
  library(patchwork)
  p <- p1+p2+p3+p4
  # Start to save figures.
  ggsave(filename= paste0(filepath, '\\Figures\\brain', name_ID12[j], 'method3.pdf'),
         plot = p,width = 10, height = 8, units = "in", dpi = 1000)
}
```
[↑ 返回目录页](#toc)<br><br>

### Work on theme{#theme}
```{Rmd}
library(ggtext)
library(rlang)
library(ggthemes)

library(ggplot2)
element_textbox_highlight <- function(..., hi.labels = NULL, hi.fill = NULL,
                                      hi.col = NULL, hi.box.col = NULL, hi.family = NULL) {
  structure(
    c(element_textbox(...),
      list(hi.labels = hi.labels, hi.fill = hi.fill, hi.col = hi.col, hi.box.col = hi.box.col, hi.family = hi.family)
    ),
    class = c("element_textbox_highlight", "element_textbox", "element_text", "element")
  )
}

strip.text1 <- element_textbox_highlight(
  family = NULL, size = 12, face = "bold",
  fill = "white", box.color = "chartreuse4", color = "black",
  halign = .5, linetype = 1, r = unit(5, "pt"), width = unit(1, "npc"),
  padding = margin(5, 0, 3, 0), margin = margin(0, 1, 3, 1),
  hi.labels = c("1997", "1998", "1999", "2000"),
  hi.fill = "chartreuse4", hi.box.col = "black", hi.col = "white"
)
# This theme's background is filled with white, boarder with black.
thmem_used <- theme(axis.text.x=element_blank(),
                    axis.text.y=element_text(size=12, color=1),
                    axis.title.x = element_text(size=12, color='black'),
                    axis.title.y = element_text(size=14, color='black'),
                    strip.text = strip.text1,#element_text(size=12),
                    legend.direction = "horizontal", legend.position = "bottom",
                    legend.text=element_text(size=15),
                    panel.background= element_rect(fill = 'white', colour = 'black'))

```
